Modelling BCG vaccination in the UK

### 2019-08-01 rmds/00-abstract.Rmd
updated abstract

Prior to the change in policy, several studies were carried out to assess the impact. The strength of this evidence has not been reassessed. I recreated one such study and found that there was a greater impact than previously thought.  \par

@@

Statistical modelling is restricted by the available data. Incorporating non-linear and indirect effects can also be complex. Therefore, I developed a dynamic model of TB, fitting to available data, and forecast the long term and indirect effects of the policy change. I found that school-age vaccination *placeholder* TB incidence rates compared with neonatal or no vaccination.

>>>>

Prior to the change in policy, several studies were carried out to assess the impact. I recreated one such study and found that there was a greater impact than previously thought. \par

@@

Statistical modelling is restricted by the available data. Therefore, I developed a dynamic model of TB, fit to available data, to forecast the impact of the policy change. Although the fit to the data was poor the forecasts suggested that continuing school-age vaccination reduced TB incidence compared with neonatal vaccination. Neonatal vaccination reduced incidence in children but had little impact on other age groups.\par
